---
title: "Iris Sepal Report"
author: "Your Name"
date: "`r Sys.Date()`"
output: pdf_document
---
  
```{r setup, include=FALSE}
# Set global chunk options to hide R code in the output
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
  
## Introduction
  
  This report provides a brief overview of the Iris dataset, focusing on sepal measurements. It includes a visualization and a summary table to illustrate key aspects of the data.

## Scatter Plot of Sepal Length vs. Sepal Width

The following scatter plot illustrates the relationship between sepal length and sepal width for different iris species.

```{r scatter-plot, fig.cap="Scatter plot of Sepal Length vs. Sepal Width"}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# Create scatter plot
ggplot(data = iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point(size = 3, alpha = 0.7) +
  labs(
    title = "Sepal Length vs. Sepal Width",
    x = "Sepal Length (cm)",
    y = "Sepal Width (cm)",
    color = "Species"
  ) +
  theme_minimal()
```
  
## Summary Table
  
  The table below summarizes the average sepal length and sepal width for each iris species.

```{r summary-table}
# Load necessary library
library(dplyr)
library(knitr)

# Create summary table
summary_table <- iris %>%
  group_by(Species) %>%
  summarize(
    Average_Sepal_Length_cm = mean(Sepal.Length, na.rm = TRUE),
    Average_Sepal_Width_cm = mean(Sepal.Width, na.rm = TRUE)
  )

# Display table
kable(summary_table, caption = "Average Sepal Length and Sepal Width by Species", 
      col.names = c("Species", "Avg Sepal Length (cm)", "Avg Sepal Width (cm)"))
```

## Conclusion
  
  This minimal report demonstrates a simple analysis of the Iris dataset, showcasing both visualization and tabular summaries of sepal measurements across different species.
