---
title: "Palmer Penguins Report"
author: "Your Name"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
# Set global chunk options to hide R code in the output
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Introduction

This report provides a brief overview of the Palmer Penguins dataset, including a visualization and a summary table.

## Scatter Plot of Flipper Length vs. Body Mass

The following scatter plot illustrates the relationship between flipper length and body mass for different penguin species.

```{r scatter-plot, fig.cap="Scatter plot of Flipper Length vs. Body Mass"}
# Load necessary libraries
library(ggplot2)
library(palmerpenguins)

# Create scatter plot
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  geom_point() +
  labs(
    title = "Flipper Length vs. Body Mass",
    x = "Flipper Length (mm)",
    y = "Body Mass (g)",
    color = "Species"
  ) +
  theme_minimal()
```

## Summary Table

The table below summarizes the average body mass and flipper length for each penguin species.

```{r summary-table}
# Load necessary libraries
library(dplyr)
library(knitr)

# Create summary table
summary_table <- penguins %>%
  group_by(species) %>%
  summarize(
    Average_Body_Mass_g = mean(body_mass_g, na.rm = TRUE),
    Average_Flipper_Length_mm = mean(flipper_length_mm, na.rm = TRUE)
  )

# Display table
kable(summary_table, caption = "Average Body Mass and Flipper Length by Species")
```

## Conclusion

This minimal report demonstrates a simple analysis of the Palmer Penguins dataset, showcasing both visualization and tabular summaries.

